A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/evaluation.tex
small change
few more corrections

We evaluated our switching planner against the baseline in several
problems with the number of rooms ranging from 3 to 6. We examine the
impact of sensing reliability, experimenting using sensor models that
are: ({\em reliable}) $0.9$ chance the object is perceived if it is
present, ({\em semi-reliable}) chance is 0.65, and ({\em noisy})
chance is 0.4. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}. Here, in switching runs we examine
the performance of our system where $b_0$ allocates non-zero
probability to between 20 and 200 abstract states during contingent
sessions. For Items~$a$-$e$ the objective is to find one or more
objects and report their position to the user. In some of the tasks we
configured the environment so that no plan exists, by excluding the
desired object from the environment. Item~$f$ reports for tasks
requiring indirect sensing, where the robot must relocate to a
particular room category. For Item~$f$ there is no human in the
environment, and therefore the baseline cannot be used, because there
are no sensing schemata that directly sense room categories. In our
evaluation we run 50 simulations in each configuration, and have a
timeout on each simulation 30 minutes (1800 seconds). In our domain,
rewards encapsulate a goal condition, and therefore we find it
intuitive to report average costs of the plans and the success rate in
problems that admit a solution (i.e., positive reward scaled by a
constant factor).

@@

Examining success ratios and plan costs, where sensing is reliable
there is little to be gained by using the contingent planner, as the
greedy sensing approach of the baseline is sufficient. Not
surprisingly, as sensing degrades contingent planning pays off.  Also,
we find that time spent in contingent planning increases steeply as
the abstraction $\bstate_0$ becomes more refined.  That refinement
seems to be paying off in terms of the success ratio, particularly for
problems $d$ and $e$, where we had sequential sessions using weighted
$A^*$ (rather than $A^*$). For less refined initial configurations, the
increase cost of contingent planning is compensated by a decrease in
time spent executing the serial system Fast Downward. The relatively
high success rate irrespective of the level of refinement in the
initial configuration indicates the effectiveness of using conditional
entropy to guide abstraction refinement in our setting.

>>>>

We evaluated our switching planner against the baseline in several
tasks with the number of rooms ranging from 3 to 6. We examine the
impact of sensing reliability, experimenting using sensor models that
are: ({\em reliable}) $0.9$ chance the object is perceived if it is
present, ({\em semi-reliable}) chance is 0.65, and ({\em noisy})
chance is 0.4. The continual planning times are reported in
Figure~\ref{fig:results-time}, and the quality data in
Figure~\ref{fig:results-quality}. Here, in switching runs we examine
the performance of our system where $b_0$ allocates non-zero
probability to between 20 and 200 abstract states during contingent
sessions. For Item~$a$-$e$ the objective is to find one or more
objects and report their position to the user. In some of the tasks we
configured the environment so that no plan exists, by excluding the
desired object from the environment. Item~$f$ reports for tasks
requiring indirect sensing, where the robot must relocate to a
particular room category. For Item~$f$ there is no human in the
environment, and therefore the baseline cannot be used, because there
are no sensing schemata that directly sense room categories. In our
evaluation we run 50 simulations in each configuration, and have a
timeout on each simulation of 30 minutes (1800 seconds). In our domain,
rewards encapsulate a goal condition, and therefore we find it
intuitive to report average costs of the plans and the success rate in
problems that admit a solution (i.e., positive reward scaled by a
constant factor).

@@

Examining success ratios and plan costs, where sensing is reliable
there is little to be gained by using the contingent planner, as the
greedy sensing approach of the baseline is sufficient. Not
surprisingly, as sensing degrades contingent planning pays off.  Also,
we find that time spent in contingent planning increases steeply as
the abstraction $\bstate_0$ becomes more refined.  That refinement
seems to be paying off in terms of the success ratio, particularly for
tasks $d$ and $e$, where we had sequential sessions using weighted
$A^*$ (rather than $A^*$). For less refined initial configurations,
the increase cost of contingent planning is compensated by a decrease
in Fast Downward planning times. The relatively high success rate
irrespective of the level of refinement in the initial configuration
indicates the effectiveness of using conditional entropy to guide
abstraction refinement in our setting.
